The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-09 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

```{r setup, echo = FALSE, message =  FALSE, warning = FALSE}
library(BSDA)
library(ggplot2)
knitr::opts_chunk$set(fig.width = 5, fig.height = 4, dpi = 300,
out.width = "90%", fig.align = "center", dev = "pdf")
```

@@

```{r table, echo = FALSE}
knitr::kable(resultsfinal, caption = 'The results from the 9 statistical tests', align = "cccccc")
```

>>>>

```{r setup, echo = FALSE, message =  FALSE, warning = FALSE}
library(BSDA)
library(ggplot2)
knitr::opts_chunk$set(fig.width = 6, fig.height = 4, dpi = 300,
out.width = "90%", fig.align = "center", dev = "pdf")
```

@@

```{r table, echo = FALSE}
knitr::kable(resultsfinal, caption = 'The results from the 9 statistical tests', align = "cccccc", booktabs = TRUE)
```
